---
title: "p8105_hw1_yy3307"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

### Problem 1

```{r import dataset}
data("penguins", package = "palmerpenguins")
```

```{r}
bill_length_mean = mean(penguins$bill_length_mm, na.rm = TRUE)
bill_depth_mean = mean(penguins$bill_depth_mm, na.rm = TRUE)
mass_mean = mean(penguins$body_mass_g, na.rm = TRUE)
```


The "penguins" dataset contains various information about 344 penguins,
which includes variables of **species, island, bill_length_mm, bill_depth_mm, 
flipper_length_mm, body_mass_g, sex, and year**. In this dataset, total number
of participants are 344 penguins. **"Species"** indicate the species of each 
penguin. The penguins can be classiffied as _3_ species: _Adelie, Chinstrap, 
and Gentoo_. **"Island"** indicate the place of origin of each 
penguin. The **"Island"** variable also has three origins: _Torgersen, Biscoe, 
and Dream_. **"bill_length_mm"** records the length of each penguin's bill, the 
average bill length of sampled penguins is 
`r round(bill_length_mean, digits = 2)`mm. **"bill_depth_mm"** holds the depth 
of each penguin's bill, the mean bill depth of sampled penguins is 
`r round(bill_depth_mean, digits = 2)`mm. **"body_mass_g"** indicates the weight
of each penguin, the average weight of sampled penguins is 
`r round(mass_mean, digits = 2)`g. Lastly, **"sex"** and **"year"** shows the 
gender and record time of each penguin.

The size of the dataset is 344 * 8, with 344 rows and 8 columns
(nrow = 344, ncol = 8).

```{r flipper mean}
flipper_mean = mean(penguins$flipper_length_mm, na.rm = TRUE)
```

The mean flipper length = `r round(flipper_mean, digits = 2)`.

```{r, warning = FALSE}
plot_penguins = tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm,
)

Species = penguins$species
ggplot(plot_penguins, aes(x = x, y = y, color = Species)) + geom_point()

ggsave("scatter_plot.pdf")
```

### Problem 2

