---
title: "p8105_hw1_yy3307"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

The first step is to load the penguins dataset:
```{r import_dataset}
data("penguins", package = "palmerpenguins")
```

### Brief description of the penguins dataset:

This code chunk is used to conduct summaries(mean) of penguins dataset:
```{r dataset_summary}
bill_length_mean = mean(penguins$bill_length_mm, na.rm = TRUE)
bill_depth_mean = mean(penguins$bill_depth_mm, na.rm = TRUE)
mass_mean = mean(penguins$body_mass_g, na.rm = TRUE)
```

The "penguins" dataset contains various information about 344 penguins,
which includes variables of **species, island, bill_length_mm, bill_depth_mm, 
flipper_length_mm, body_mass_g, sex, and year**. In this dataset, total number
of participants are 344 penguins. **"Species"** indicate the species of each 
penguin. The penguins can be classiffied as _3_ species: _Adelie, Chinstrap, 
and Gentoo_. **"Island"** indicate the place of origin of each 
penguin. The **"Island"** variable also has three origins: _Torgersen, Biscoe, 
and Dream_. **"bill_length_mm"** records the length of each penguin's bill, the 
average bill length of sampled penguins is 
`r round(bill_length_mean, digits = 2)` mm. **"bill_depth_mm"** holds the depth 
of each penguin's bill, the mean bill depth of sampled penguins is 
`r round(bill_depth_mean, digits = 2)` mm. **"body_mass_g"** indicates the 
weight of each penguin, the average weight of sampled penguins is 
`r round(mass_mean, digits = 2)` g. Lastly, **"sex"** and **"year"** shows the 
gender and record time of each penguin.

### Size of the dataset:

The size of the dataset is 344 * 8, with 344 rows and 8 columns
(nrow = 344, ncol = 8).

### Mean flipper length:

Calculate average of flipper_length_mm column (NA skipped):
```{r flipper_mean}
flipper_mean = mean(penguins$flipper_length_mm, na.rm = TRUE)
```

The mean flipper length = `r round(flipper_mean, digits = 2)` mm.

### Create a scatter plot with condition and export it.

```{r scatter_plot, warning = FALSE}
plot_penguins = tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm,
)

Species = penguins$species
ggplot(plot_penguins, aes(x = x, y = y, color = Species)) + geom_point() + labs(title = "bill length v.s. flipper length", x = "bill length (mm)", y = "flipper length (mm)") + theme(plot.title = element_text(hjust = 0.5))

ggsave("scatter_plot.pdf")
```

# Problem 2

### Create date frame.

Code chunk below is the dataframe setting:
```{r df_setting}
q2_df = tibble(
  random_sample = rnorm(10),
  vec_logic = random_sample > 0,
  vec_char = c("One", "Two", "Three", "Four", "Five", "Six", "Seven", "Eight", "Nine", "Ten"),
  vec_factor = factor(c("High", "Medium", "Low", "High", "Medium", "Low","High", "Medium", "Low","High"))
)
```

Then, we will test if each variables in the dataframe has a mean value.
```{r mean_df_var}
mean(pull(q2_df, random_sample))
mean(pull(q2_df, vec_logic))
mean(pull(q2_df, vec_char))
mean(pull(q2_df, vec_factor))
```

From the output we can analyse that we are able to calculate the mean value for 
numeric variables "random_sample" and "vec_logic". However, we cannot find the 
mean value for "vec_char" and "vec_factor" since they are not in numerical expression.
So when I tried to find mean value for these two variables, I will receive _NA_
as result.

Next, I'm going to apply as.numeric function to logic, char, and factor variables.
```{r convert, eval = FALSE}
as.numeric(pull(q2_df, vec_logic))
as.numeric(pull(q2_df, vec_char))
as.numeric(pull(q2_df, vec_factor))
```

The output indicates that we can convert logic variables and factor variables
into numerical expression, but we can't convert character vector as numeric.
Logic variables will be transferred into 0 and 1 after convertion, and factor
variables will be transferred into numbers starting from 1 according to their
factor “levels” in alphabetical order.
This result also shows that the output will fill up with _NA_ variables as place
holders if the function cannot apply to the situation. That's the reason why I 
received NA as the output of two mean values of non numeric vactors.